Pure Spin Current Injection in Hydrogenated Graphene Structures

### 2017-04-04 mu/article/article.tex
Makkng layer divisions in structures.
Changing format to revtex4-1

@@

\textcolor{red}{
{\huge Filling with text.}\\
\blindtext
}
\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{figures/altstruc1}
    \includegraphics[width=\linewidth]{figures/altstruc2}
    \caption{Alt structure.}
    \label{fig:altstruc}
\end{figure}
\begin{figure}[h!]
    \centering
    \includegraphics[width=\linewidth]{figures/upstruc1}
    \includegraphics[width=\linewidth]{figures/upstruc2}
    \caption{Up structure}
    \label{fig:upstruc}
\end{figure}
% \begin{figure}[h]
%     \centering
%     \includegraphics[width=\linewidth]{figures/hnbGh-aa-1}
%     \includegraphics[width=\linewidth]{figures/hnbGh-aa-2}
%     \caption{HNBC$_{2}$H-aa structure}
%     \label{fig:aastruc}
% \end{figure}
% \begin{figure}[h]
%     \centering
%     \includegraphics[width=\linewidth]{figures/hnbGh-ab-1}
%     \includegraphics[width=\linewidth]{figures/hnbGh-ab-2}
%     \caption{HNBC$_{2}$H-ab structure}
%     \label{fig:abstruc}
% \end{figure}

@@

We also define $|\mathcal{V}^{\mathrm{a}}|$ as 
\begin{equation}\label{eq:vab-mag}
|\mathcal{V}^{\mathrm{a}}| = 
\sqrt {
(\mathcal{V}^{\mathrm{ax}})^{2} +
(\mathcal{V}^{\mathrm{ay}})^{2} +
(\mathcal{V}^{\mathrm{az}})^{2} 
},
\end{equation}
and the corresponding polar and azimuthal angles $\theta$ and $\varphi$ as
\begin{align}
\theta  =& \cos^{-1} \left(  \frac{\mathcal{V}^{\mathrm{az}}}
{|\mathcal{V}^{\mathrm{a}}|} \right),
& 0 \leq &\theta \leq \pi, 
\label{eq:polar-ang} \\
\varphi =& \tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{ay}}}{\mathcal{V}^{\mathrm{ax}}} \right),
& 0 \leq &\varphi \leq 2\pi. \\ 
\label{eq:azimuthal-ang} 
\end{align}

@@

\begin{table}[tb]
\center
\begin{tabular}{ccccc}\\
\hline
Layer & Atom & \multicolumn{3}{c}{Position [\AA]} \\
\cline{3-5}
No. & type & $x$ & $y$ & $z$  \\
\hline
1 & H &  -0.61516 &  -1.42140 & \ 1.47237 \\
2 & C &  -0.61516 &  -1.73300 & \ 0.39631 \\
3 & C & \ 0.61516 & \ 1.73300 & \ 0.15807 \\
4 & C & \ 0.61516 & \ 0.42201 &  -0.15814 \\
5 & C &  -0.61516 &  -0.37396 &  -0.39632 \\
6 & H &  -0.61516 &  -0.68566 &  -1.47237 \\
\hline
\end{tabular}
\caption{Unit cell of \emph{alt} structure. Layer division, atom types and
positions for the \emph{alt} structure. The structure unit cell was divided in
six layers corresponding each one to atoms in different $z$ positions.}
\label{tab:altunitcell}
\end{table}

The structures presented here where divided into layers to analyze the he layer-
by-layer contribution for $\mathcal{V}^{\mathrm{ab}}$ response. The \emph{alt}
structure was divided in six layers corresponding the first one to the top
hydrogen atoms, from the second to the forth to carbon atoms in different $z$
positions, and the sixth and last one to the bottom hydrogen atoms. The
\emph{up} structure was divided into two layers, the first one comprised by the
top hydrogen atoms and the second by the carbon atoms. The layer divisions and
atom positions for the unit cells are shown in Tables \ref{tab:altunitcell} and
\ref{tab:upunitcell}.

\begin{table}[tb]
\center
\begin{tabular}{ccccc}\\
\hline
Layer & Atom & \multicolumn{3}{c}{Position [\AA]} \\
\cline{3-5}
No. & type & $x$ & $y$ & $z$  \\
\hline
1 & H & -0.61516 & -1.77416 &  0.73196 \\
1 & H &  0.61518 &  0.35514 &  0.73175 \\
2 & C & -0.61516 & -1.77264 & -0.49138 \\
2 & C & -0.61516 & -0.35600 & -0.72316 \\
2 & C &  0.61516 &  0.35763 & -0.49087 \\
\hline
\end{tabular}
\caption{Unit cell of \emph{up} structure. Layer division, atom types and
positions for the \emph{up} structure. The structure unit cell was divided in
two layers corresponding to hydrogen and carbon atoms.}
\label{tab:upunitcell}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% ALT %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{alt} % (fold)
\label{sec:results-alt}

In Fig. \ref{fig:alt-magvxbincang} we present the $\mathcal{V}^{\mathrm{x}}$
spectra resulting from evaluate the Eq. \eqref{eq:vab-mag} at using different
polarization angles $\alpha$ in Eq. \eqref{eq:vab} for the C$_16$H$_8$-alt
structure. The onset of the response is when the energy of the incoming light is
the same of the gap energy. From this picture we can see that for the zone
between the energy range of 0.90\,eV-0.93\,eV and polarization angles between
120$^{\circ}$ and 150$^{\circ}$ is the zone of the maximum response is held
reaching values of $\mathcal{V}^{\mathrm{x}}$ near to 30\,Km/s. Also there is a
second zone between the energy range of 0.70\,eV-0.74\,eV and same polarization
angles where a local maximum of $\mathcal{V}^{\mathrm{x}}$ reaching values near
to 22\,Km/s.We also found that the absolute maximum of the response is obtained
for a polarization angle $\alpha = 145^{\circ}$. The decomposition of
$|\mathcal{V}^{\mathrm{a}}|$ in the corresponding $\mathcal{V}^{\mathrm{x}}$,
$\mathcal{V}^{\mathrm{y}}$, and $\mathcal{V}^{\mathrm{z}}$ components is
depicted in Fig. \ref{fig:alt-vxb}. From this figure we can see that for the
energy range from 0.70\,eV to 0.74\,eV all the $x$, $y$, and $z$ components
contribute with almost the same intensity. In the other hand, for the energy
range from 0.88\,eV to 0.95\,eV there is a major contribution coming from the
$\mathcal{V}^{\mathrm{xz}}$ component.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% xb [0.6:1.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{$\mathcal{V}^{\mathrm{x}}$}
\begin{figure}[]
    \centering
    \includegraphics[width=\linewidth]{altplots/alt-magvxb-incang-4545.pdf}
    \caption{$\mathcal{V}^{\mathrm{x}}$ for C$_16$H$_8$-alt structure. The
    maximum response zone is localized for an energy range from 0.90\,eV to
    0.93\,eV. 145$^{\circ}$ and for a polarization angle of the incoming beam from 120$^{\circ}$ to 150$^{\circ}$.}
    \label{fig:alt-magvxbincang}
\end{figure}

\begin{figure}[]
    \centering
    \includegraphics[width=\linewidth]{altplots/alt-vab-xb.pdf}
    \caption{Three components of $\mathcal{V}^{\mathrm{x}} $ @ 145$^{\circ}$.}
    \label{fig:alt-vxb}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% yb [0.6:1.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{$\mathcal{V}^{\mathrm{y}}$}
\begin{figure}[ht]
    \centering
    \includegraphics[width=\linewidth]{altplots/alt-magvyb-incang-4545.pdf}
    \caption{The most intense response for $\mathcal{V}^{\mathrm{y}} $ is for 
    145$^{\circ}$.}
    \label{fig:alt-magvybincang1}
\end{figure}
\begin{figure}[ht]
    \centering
    \includegraphics[width=\linewidth]{altplots/alt-vxx.pdf}
    \includegraphics[width=\linewidth]{altplots/alt-vxy.pdf}\\
    \includegraphics[width=\linewidth]{altplots/alt-vxz.pdf}
    \caption{Cheking angle of incidence for $yb$ components.}
    \label{fig:alt-ybangcomp}
\end{figure}
\begin{figure}[ht]
    \centering
    \includegraphics[width=\linewidth]{altplots/alt-vab-yb.pdf}
    \caption{Three components of $\mathcal{V}^{\mathrm{y}} $ @ 145$^{\circ}$.}
    \label{fig:alt-vyb1}
\end{figure}

%%%%%%%%%%%%%%%%%%%%% |V^{ab}| [0.6:1.0] rtp comp %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{$|\mathcal{V}^{\mathrm{ab}}|$, angles
$\theta$ and $\varphi$, layers, and comparison with CdSe and GaAs.}
\begin{figure}[ht]
    \centering
    \includegraphics[width=\linewidth]{altplots/alt-vxb-rtp.pdf}
    \includegraphics[width=\linewidth]{altplots/alt-vyb-rtp.pdf}
    \caption{$|\mathcal{V}^{\mathrm{ab}}|$ (solid line, leftside scale) and the
    corresponding angles $\theta$ and $\varphi$ (dashed lines, rightside scale).}
    \label{fig:alt-rtp}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[width=\linewidth]{altplots/alt-vyz-layers.pdf}
    \caption{Layer decomposition for the most intense response:
    $\mathcal{V}^{\mathrm{yz}}$.}
    \label{fig:alt-lay}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[width=\linewidth]{altplots/alt-vab-comp.pdf}
    \caption{Comparisson of the most intense response vs the most intense
    responses of CdSe and GaAs.}
    \label{fig:alt-comp}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[width=\linewidth]{altplots/alt-absvab.pdf}
    \caption{Comparisson of $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$}    
    \label{fig:alt-xbybcomp}
\end{figure}

% subsection alt (end)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% UP %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Up (graphone)} % (fold)
\label{sec:results-up}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% xb [0.0:0.2] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{$\mathcal{V}^{\mathrm{x}}$ energy range 0.0--0.2 eV }
\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-magvxb-incang-1-4545.pdf}
    \caption{The most intense response for $\mathcal{V}^{\mathrm{x}} $ is for 
    40$^{\circ}$.}
    \label{fig:up-magvxbincang1}
\end{figure}
\begin{figure}[ht]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-vab-xx-angcomp.pdf}
    \includegraphics[width=\linewidth]{upplots/up-vab-xy-angcomp.pdf}\\
    \includegraphics[width=\linewidth]{upplots/up-vab-xz-angcomp.pdf}
    \caption{Cheking angle of incidence for $xb$ components for up structure.}
    \label{fig:up-xbangcomp}
\end{figure}
\begin{figure}[tb]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-vab-xb-1.pdf}
    \caption{Three components of $\mathcal{V}^{\mathrm{x}} $ @ 40$^{\circ}$.}
    \label{fig:up-vxb1}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% yb [0.0:0.2] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{$\mathcal{V}^{\mathrm{y}}$ energy range 0.0--0.2 eV }
\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-magvyb-incang-1-4545.pdf}
    \caption{The most intense response for $\mathcal{V}^{\mathrm{y}} $ is for 
    40$^{\circ}$.}
    \label{fig:up-magvybincang1}
\end{figure}
\begin{figure}[ht]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-vab-yx-angcomp.pdf}
    \includegraphics[width=\linewidth]{upplots/up-vab-yy-angcomp.pdf}\\
    \includegraphics[width=\linewidth]{upplots/up-vab-yz-angcomp.pdf}
    \caption{Cheking angle of incidence for $yb$ components.}
    \label{fig:up-ybangcomp}
\end{figure}
\begin{figure}[ht]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-vab-yb-1.pdf}
    \caption{Three components of $\mathcal{V}^{\mathrm{y}} $ @ 40$^{\circ}$.}
    \label{fig:up-vyb1}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-absvab-1.pdf}
    \caption{Comparisson of $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$}    
    \label{fig:up-xbybcomp-1}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% xb [1.8:2.1] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{$\mathcal{V}^{\mathrm{x}}$ energy range 1.8--2.1 eV }

\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-magvxb-incang-2-4545.pdf}
    \caption{The most intense response for $\mathcal{V}^{\mathrm{x}} $ is for 
    40$^{\circ}$.}
    \label{fig:up-magxbincang2}
\end{figure}
\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-vab-xb-2.pdf}
    \caption{Three components of $\mathcal{V}^{\mathrm{x}} $ @ 40$^{\circ}$.}
    \label{fig:up-vxb2}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-magvyb-incang-2-4545.pdf}
    \caption{The most intense response for $\mathcal{V}^{\mathrm{y}} $ is for 
    40$^{\circ}$.}
    \label{fig:up-magybincang2}
\end{figure}
\begin{figure}[ht]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-vab-yb-2.pdf}
    \caption{Three components of $\mathcal{V}^{\mathrm{y}} $ @ 40$^{\circ}$.}
    \label{fig:upvyb2}
\end{figure}

\clearpage

%%%%%%%%%%%%%%%%%%%%% |V^{ab}| [0.0:0.2] rtp comp %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{$|\mathcal{V}^{\mathrm{ab}}|$, angles
$\theta$ and $\varphi$, layers, and comparison with CdSe and GaAs for the energy
range of 0.0--0.2 eV.}

\begin{figure}[ht]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-vxb-rtp-1.pdf}
    \includegraphics[width=\linewidth]{upplots/up-vyb-rtp-1.pdf}
    \caption{$|\mathcal{V}^{\mathrm{ab}}|$ (solid line, leftside scale) and the
    corresponding angles $\theta$ and $\varphi$ (dashed lines, rightside scale).}
    \label{fig:up-rtp1}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-vyz-layers-1.pdf}
    \caption{Layer decomposition for the most intense response:
    $\mathcal{V}^{\mathrm{yz}}$.}
    \label{fig:up-lay1}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-vab-yz-comp-1.pdf}
    \caption{Comparisson of the most intense response vs the most intense
    responses of CdSe and GaAs.}
    \label{fig:up-comp1}
\end{figure}

%%%%%%%%%%%%%%%%%%%%% |V^{ab}| [1.8:2.1] rtp comp %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{$|\mathcal{V}^{\mathrm{ab}}|$, angles
$\theta$ and $\varphi$, layers, and comparison with CdSe and GaAs for the energy
range of 1.8--2.1 eV}

>>>>

\section{abstract} % (fold)
\label{sec:abstract}
\textcolor{red}{{\huge Filling with text.}\\ \blindtext}
% section abstract (end)

@@

\textcolor{red}{\blindtext}
\begin{figure}[ht!]
    \centering
    \includegraphics[width=\linewidth]{figures/altstruc2}
    \includegraphics[width=\linewidth]{figures/altstruc1}
    \caption{Alt structure.}
    \label{fig:altstruc}
\end{figure}
\begin{figure}[ht!]
    \centering
    \includegraphics[width=\linewidth]{figures/upstruc2}
    \includegraphics[width=\linewidth]{figures/upstruc1}
    \caption{Up structure}
    \label{fig:upstruc}
\end{figure}
% \begin{figure}[tb]
%     \centering
%     \includegraphics[width=\linewidth]{figures/hnbGh-aa-1}
%     \includegraphics[width=\linewidth]{figures/hnbGh-aa-2}
%     \caption{HNBC$_{2}$H-aa structure}
%     \label{fig:aastruc}
% \end{figure}
% \begin{figure}[tb]
%     \centering
%     \includegraphics[width=\linewidth]{figures/hnbGh-ab-1}
%     \includegraphics[width=\linewidth]{figures/hnbGh-ab-2}
%     \caption{HNBC$_{2}$H-ab structure}
%     \label{fig:abstruc}
% \end{figure}

@@

We also define $|\mathcal{V}^{\mathrm{a}}|$ as 
\begin{equation}\label{eq:va-mag}
|\mathcal{V}^{\mathrm{a}}| = 
\sqrt {
(\mathcal{V}^{\mathrm{ax}})^{2} +
(\mathcal{V}^{\mathrm{ay}})^{2} +
(\mathcal{V}^{\mathrm{az}})^{2} 
},
\end{equation}
and the corresponding polar and azimuthal angles $\theta$ and $\varphi$ as
\begin{align}
\theta  =& \cos^{-1} \left(  \frac{\mathcal{V}^{\mathrm{az}}}
{|\mathcal{V}^{\mathrm{a}}|} \right),
& 0 \leq &\theta \leq \pi, 
\label{eq:polar-ang} \\
\varphi =& \tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{ay}}}{\mathcal{V}^{\mathrm{ax}}} \right),
& 0 \leq &\varphi \leq 2\pi. \\ 
\label{eq:azimuthal-ang} 
\end{align}

@@

\begin{table}[tb]
\center
\begin{tabular}{ccccc}\\
\hline
Layer & Atom & \multicolumn{3}{c}{Position [\AA]} \\
\cline{3-5}
No. & type & $x$ & $y$ & $z$  \\
\hline
1 & H &  -0.61516 &  -1.42140 & \ 1.47237 \\
2 & C &  -0.61516 &  -1.73300 & \ 0.39631 \\
3 & C & \ 0.61516 & \ 1.73300 & \ 0.15807 \\
4 & C & \ 0.61516 & \ 0.42201 &  -0.15814 \\
5 & C &  -0.61516 &  -0.37396 &  -0.39632 \\
6 & H &  -0.61516 &  -0.68566 &  -1.47237 \\
\hline
% \multicolumn{5}{c}{\includegraphics[width=0.4\linewidth]{figures/alt-unitcell-layers.pdf}} \\
% \hline
\end{tabular}
\caption{Unit cell of \emph{alt} structure. Layer division, atom types and
positions for the \emph{alt} structure. The structure unit cell was divided in
six layers corresponding each one to atoms in different $z$ positions. The
corresponding layer atom position is depicted in Fig. \ref{fig:altstruc} with
the corresponding number of layer.}
\label{tab:alt-unitcell}
\end{table}

The structures presented here where divided into layers to analyze the he layer-
by-layer contribution for $\mathcal{V}^{\mathrm{ab}}$ response. The \emph{alt}
structure was divided in six layers corresponding the first one to the top
hydrogen atoms, from the second to the forth to carbon atoms in different $z$
positions, and the sixth and last one to the bottom hydrogen atoms. The
\emph{up} structure was divided into two layers, the first one comprised by the
top hydrogen atoms and the second by the carbon atoms. The layer divisions and
atom positions for the unit cells are shown in Tables \ref{tab:alt-unitcell} and
\ref{tab:up-unitcell}.

\begin{table}[tb]
\center
\begin{tabular}{ccccc}\\
\hline
Layer & Atom & \multicolumn{3}{c}{Position [\AA]} \\
\cline{3-5}
No. & type & $x$ & $y$ & $z$  \\
\hline
1 & H & -0.61516 & -1.77416 &  0.73196 \\
1 & H &  0.61518 &  0.35514 &  0.73175 \\
2 & C & -0.61516 & -1.77264 & -0.49138 \\
2 & C & -0.61516 & -0.35600 & -0.72316 \\
2 & C &  0.61516 &  0.35763 & -0.49087 \\
\hline
\end{tabular}
\caption{Unit cell of \emph{up} structure. Layer division, atom types and
positions for the \emph{up} structure. The structure unit cell was divided in
two layers corresponding to hydrogen and carbon atoms.The corresponding layer
atom position is depicted in Fig. \ref{fig:upstruc} with the corresponding
number of layer.}
\label{tab:up-unitcell}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% ALT %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{alt} % (fold)
\label{sec:results-alt}

For the \emph{alt} structure we analized the energby range from 0.6\,eV to
1.0\,eV where we found the major response for $\mathcal{V}^{\mathrm{ab}}$ and
$|\mathcal{V}^{\mathrm{a}}|$. In Fig. \ref{fig:alt-magvxbincang} we present the
$|\mathcal{V}^{\mathrm{x}}|$ spectra resulting from evaluate Eq.
\eqref{eq:va-mag} using different polarization angles $\alpha$ in Eq.
\eqref{eq:vab} forthe C$_{16}$H$_{8}$-alt structure. The onset of the response
is when the energy of the incoming light is the same of the gap energy. From
this picture we can see that for the zone between the energy range of
0.90\,eV-0.93\,eV and polarization angles between 120$^{\circ}$ and
150$^{\circ}$ is the zone of the maximum response is held reaching
$|\mathcal{V}^{\mathrm{x}}|$ values of near to 30\,Km/s. Also there is a second
zone between the energy range of 0.70\,eV-0.74\,eV and same polarization angles
where a local maximum of $\mathcal{V}^{\mathrm{x}}$ reaching values near to
22\,Km/s.We also found that the absolute maximum of the response is obtained for
a polarization angle $\alpha = 145^{\circ}$. The decomposition of
$|\mathcal{V}^{\mathrm{a}}|$ in the corresponding $\mathcal{V}^{\mathrm{x}}$,
$\mathcal{V}^{\mathrm{y}}$, and $\mathcal{V}^{\mathrm{z}}$ components is
depicted in Fig. \ref{fig:alt-vxb}. From this figure we can see that for the
energy range from 0.70\,eV to 0.74\,eV all the $x$, $y$, and $z$ components
contribute with almost the same intensity. In the other hand, for the energy
range from 0.88\,eV to 0.95\,eV there is a major contribution coming from the
$\mathcal{V}^{\mathrm{xz}}$ component.

%%%%%%%%%%%%%%%%%%%%%%%%%%% xb [0.6:1.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{$\mathcal{V}^{\mathrm{x}}$}
\begin{figure}[tb]
    \centering
    \includegraphics[width=\linewidth]{altplots/alt-magvxb-incang-4545.pdf}
    \includegraphics[width=\linewidth]{altplots/alt-magvyb-incang-4545.pdf}  
    \caption{$|\mathcal{V}^{\mathrm{x}}|$ response for C$_{16}$H$_{8}$-alt structure. The
    maximum response zone is localized for an energy range from 0.90\,eV to
    0.93\,eV. 145$^{\circ}$ and for a polarization angle of the incoming beam from 120$^{\circ}$ to 150$^{\circ}$.}
    \label{fig:alt-magvxbincang}
\end{figure}
\begin{figure}[tb]
    \centering
    \includegraphics[width=\linewidth]{altplots/alt-vab-xb.pdf}
    \caption{Three components of $\mathcal{V}^{\mathrm{x}} $ @ 145$^{\circ}$.}
    \label{fig:alt-vxb}
\end{figure}

% %%%%%%%%%%%%%%%%%%%%%%%%%%% yb [0.6:1.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{$\mathcal{V}^{\mathrm{y}}$}
% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=\linewidth]{altplots/alt-magvyb-incang-4545.pdf}
%     \caption{The most intense response for $\mathcal{V}^{\mathrm{y}} $ is for 
%     145$^{\circ}$.}
%     \label{fig:alt-magvybincang1}
% \end{figure}
% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=\linewidth]{altplots/alt-vxx.pdf}
%     \includegraphics[width=\linewidth]{altplots/alt-vxy.pdf}\\
%     \includegraphics[width=\linewidth]{altplots/alt-vxz.pdf}
%     \caption{Cheking angle of incidence for $yb$ components.}
%     \label{fig:alt-ybangcomp}
% \end{figure}
% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=\linewidth]{altplots/alt-vab-yb.pdf}
%     \caption{Three components of $\mathcal{V}^{\mathrm{y}} $ @ 145$^{\circ}$.}
%     \label{fig:alt-vyb1}
% \end{figure}

% %%%%%%%%%%%%%%%%%%% |V^{ab}| [0.6:1.0] rtp comp %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{$|\mathcal{V}^{\mathrm{ab}}|$, angles
% $\theta$ and $\varphi$, layers, and comparison with CdSe and GaAs.}
% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=\linewidth]{altplots/alt-vxb-rtp.pdf}
%     \includegraphics[width=\linewidth]{altplots/alt-vyb-rtp.pdf}
%     \caption{$|\mathcal{V}^{\mathrm{ab}}|$ (solid line, leftside scale) and the
%     corresponding angles $\theta$ and $\varphi$ (dashed lines, rightside scale).}
%     \label{fig:alt-rtp}
% \end{figure}

% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=\linewidth]{altplots/alt-vyz-layers.pdf}
%     \caption{Layer decomposition for the most intense response:
%     $\mathcal{V}^{\mathrm{yz}}$.}
%     \label{fig:alt-lay}
% \end{figure}

% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=\linewidth]{altplots/alt-vab-comp.pdf}
%     \caption{Comparisson of the most intense response vs the most intense
%     responses of CdSe and GaAs.}
%     \label{fig:alt-comp}
% \end{figure}

% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=\linewidth]{altplots/alt-absvab.pdf}
%     \caption{Comparisson of $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$}    
%     \label{fig:alt-xbybcomp}
% \end{figure}

% % subsection alt (end)

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% UP %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsection{Up (graphone)} % (fold)
% \label{sec:results-up}

% %%%%%%%%%%%%%%%%%%%%%%%%%%% xb [0.0:0.2] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \subsubsection{$\mathcal{V}^{\mathrm{x}}$ energy range 0.0--0.2 eV }
% \begin{figure}[tb]
%     \centering
%     \includegraphics[width=\linewidth]{upplots/up-magvxb-incang-1-4545.pdf}
%     \caption{The most intense response for $\mathcal{V}^{\mathrm{x}} $ is for 
%     40$^{\circ}$.}
%     \label{fig:up-magvxbincang1}
% \end{figure}
% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=\linewidth]{upplots/up-vab-xx-angcomp.pdf}
%     \includegraphics[width=\linewidth]{upplots/up-vab-xy-angcomp.pdf}\\
%     \includegraphics[width=\linewidth]{upplots/up-vab-xz-angcomp.pdf}
%     \caption{Cheking angle of incidence for $xb$ components for up structure.}
%     \label{fig:up-xbangcomp}
% \end{figure}
% \begin{figure}[tb]
%     \centering
%     \includegraphics[width=\linewidth]{upplots/up-vab-xb-1.pdf}
%     \caption{Three components of $\mathcal{V}^{\mathrm{x}} $ @ 40$^{\circ}$.}
%     \label{fig:up-vxb1}
% \end{figure}

% %%%%%%%%%%%%%%%%%%%%%%%%%%% yb [0.0:0.2] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \subsubsection{$\mathcal{V}^{\mathrm{y}}$ energy range 0.0--0.2 eV }
% \begin{figure}[tb]
%     \centering
%     \includegraphics[width=\linewidth]{upplots/up-magvyb-incang-1-4545.pdf}
%     \caption{The most intense response for $\mathcal{V}^{\mathrm{y}} $ is for 
%     40$^{\circ}$.}
%     \label{fig:up-magvybincang1}
% \end{figure}
% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=\linewidth]{upplots/up-vab-yx-angcomp.pdf}
%     \includegraphics[width=\linewidth]{upplots/up-vab-yy-angcomp.pdf}\\
%     \includegraphics[width=\linewidth]{upplots/up-vab-yz-angcomp.pdf}
%     \caption{Cheking angle of incidence for $yb$ components.}
%     \label{fig:up-ybangcomp}
% \end{figure}
% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=\linewidth]{upplots/up-vab-yb-1.pdf}
%     \caption{Three components of $\mathcal{V}^{\mathrm{y}} $ @ 40$^{\circ}$.}
%     \label{fig:up-vyb1}
% \end{figure}

% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=\linewidth]{upplots/up-absvab-1.pdf}
%     \caption{Comparisson of $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$}    
%     \label{fig:up-xbybcomp-1}
% \end{figure}

% %%%%%%%%%%%%%%%%%%%%%%%%%%% xb [1.8:2.1] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \subsubsection{$\mathcal{V}^{\mathrm{x}}$ energy range 1.8--2.1 eV }

% \begin{figure}[tb]
%     \centering
%     \includegraphics[width=\linewidth]{upplots/up-magvxb-incang-2-4545.pdf}
%     \caption{The most intense response for $\mathcal{V}^{\mathrm{x}} $ is for 
%     40$^{\circ}$.}
%     \label{fig:up-magxbincang2}
% \end{figure}
% \begin{figure}[tb]
%     \centering
%     \includegraphics[width=\linewidth]{upplots/up-vab-xb-2.pdf}
%     \caption{Three components of $\mathcal{V}^{\mathrm{x}} $ @ 40$^{\circ}$.}
%     \label{fig:up-vxb2}
% \end{figure}

% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=\linewidth]{upplots/up-magvyb-incang-2-4545.pdf}
%     \caption{The most intense response for $\mathcal{V}^{\mathrm{y}} $ is for 
%     40$^{\circ}$.}
%     \label{fig:up-magybincang2}
% \end{figure}
% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=\linewidth]{upplots/up-vab-yb-2.pdf}
%     \caption{Three components of $\mathcal{V}^{\mathrm{y}} $ @ 40$^{\circ}$.}
%     \label{fig:upvyb2}
% \end{figure}

% %%%%%%%%%%%%%%%%%%% |V^{ab}| [0.0:0.2] rtp comp %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{$|\mathcal{V}^{\mathrm{ab}}|$, angles
% $\theta$ and $\varphi$, layers, and comparison with CdSe and GaAs for the energy
% range of 0.0--0.2 eV.}

% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=\linewidth]{upplots/up-vxb-rtp-1.pdf}
%     \includegraphics[width=\linewidth]{upplots/up-vyb-rtp-1.pdf}
%     \caption{$|\mathcal{V}^{\mathrm{ab}}|$ (solid line, leftside scale) and the
%     corresponding angles $\theta$ and $\varphi$ (dashed lines, rightside scale).}
%     \label{fig:up-rtp1}
% \end{figure}
